Final Project - Stroke Predictions

### 2021-05-14 draft.Rmd
overall health

### Prep the data
```{r, echo=TRUE}
stroke = stroke %>%
  select(-id)

@@

>>>>

### Prep the data
```{r, echo=TRUE}

stroke = read_csv("stroke.csv")

@@

## Overall Health
```{r, echo=TRUE}
# create data set
stroke_single = stroke_factor %>%
  select(hypertension, heart_disease, avg_glucose_level, smoking_status, stroke) %>%
  mutate(hypertension = as.factor(hypertension)) %>%
  mutate(stroke = as.factor(stroke)) %>%
  mutate(heart_disease = as.factor(heart_disease))

stroke_single$avg_glucose_level <- factor(ifelse(as.double(stroke_factor$avg_glucose_level)>=106.15, "high", "low"))

stroke_single$smoking_status = fct_collapse(
  stroke_factor$smoking_status,
  "1" = c("formerly smoked", "smokes"),
  "0" = c("never smoked", "Unknown")
)

stroke_single = stroke_single %>%
  mutate(hypertension = as.numeric(hypertension)-1) %>%
  mutate(heart_disease = as.numeric(heart_disease)-1) %>%
  mutate(avg_glucose_level = as.numeric(avg_glucose_level)-1) %>%
  mutate(smoking_status = as.numeric(smoking_status)-1) %>%
  mutate(unhealthy = hypertension + heart_disease + avg_glucose_level + smoking_status)

stroke_single = stroke_single %>%
  mutate(unhealthy = 
           if_else(
              unhealthy >=1, "1", "0",

  )
  ) %>%
  mutate(unhealthy=as.factor(unhealthy)) %>%
  select(unhealthy, stroke)

datatable(stroke_single)

correlation = cor.test(as.numeric(stroke_single$stroke), as.numeric(stroke_single$unhealthy), method="pearson")
correlation
```

The correlation between being 'unhealthy' and having a stroke is `r correlation$estimate`

This is strange as we would expect there to be a positive correlation, not a negative one. This goes to show that we cannot always trust simple correlation analysis.
